\documentclass[a4paper,12pt]{article}
\usepackage[english,vietnamese]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{forest}
\usepackage{textcomp}
\usepackage[nottoc,numbib]{tocbibind}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\begin{document}
\setcounter{page}{0}
\thispagestyle{empty}
\vspace*{\stretch{1}}
\begin{flushright}
  \setlength{\baselineskip}{1.4\baselineskip}
\textbf{\Huge Final Report\\Speaker Recognition}
  \noindent\rule{\textwidth}{5pt}
  \emph{\Large Digital Signal Processing}
  \vspace{\stretch{1}}

  \textbf{by Vũ Vương Quốc Anh, Phạm Minh Long, Hoàng Nhật Tân,\\
          Nguyễn Trường Giang, Đỗ Đức Mạnh, Trần Minh Vương,\\
          Nguyễn Minh Hoàng, Nguyễn Gia Phong and Nguyễn An Thiết\\}
  \selectlanguage{english}
  \today
\end{flushright}
\vspace*{\stretch{2}}
\pagebreak

\selectlanguage{english}
\tableofcontents
\pagebreak

\section{Introduction}
\subsection{Brief Description}
This report is licensed under a
\href{http://creativecommons.org/licenses/by-sa/4.0/}{Creative Commons
Attribution-ShareAlike 4.0 International License.}

\selectlanguage{vietnamese}
\subsection{Authors and Credits}
The work has been undertaken by group number 6, whose members are listed
in the following table.
\begin{center}
  \begin{tabular}{c c}
    \toprule
    Full name & Student ID\\
    \midrule
    Vũ Vương Quốc Anh & BI9-046\\
    Nguyễn Trường Giang & BI9-084\\
    Nguyễn Minh Hoàng & BI9-108\\
    Phạm Minh Long & BI9-146\\
    Đỗ Đức Mạnh & BI9-163\\
    Nguyễn Gia Phong & BI9-184\\
    Hoàng Nhật Tân & BI9-205\\
    Trần Minh Vương & BI9-239\\
    Nguyễn An Thiết & BI8-174\\
    \bottomrule
  \end{tabular}
\end{center}

We would like to express our special thanks to Dr. Trần Hoàng Tùng,
whose lectures gave us basic understanding on the key principles of
digital signal processing.  Without his guidance, we might never
have a chance to take an in-depth exploration on this topic.
\pagebreak

\selectlanguage{english}
\section{Conclusion}
\pagebreak

\begin{thebibliography}{99}
  \bibitem{wu} C. Thomas Wu.
    \emph{\href{https://users.cs.duke.edu/~ola/bubble/bubble.html}{Bubble Sort: An Archaeological Algorithmic Analysis}}.
    Duke University.
  \bibitem{peculiar} Donald E. Knuth.  The Dangers of Computer-Science Theory.
    \emph{Studies in Logic and the Foundations of Mathematics}, vol. 74.
    Elsevier, 1973.
    doi:\href{https://doi.org/10.1016/S0049-237X(09)70357-X}{10.1016/S0049-237X(09)70357-X}.
  \bibitem{old} \href{https://en.wikipedia.org/wiki/Lists_of_state_leaders_by_age#10_oldest_currently_serving_state_leaders}{Lists of state leaders by age}.
    \emph{Wikipedia}.
    Section 1: \emph{10 oldest currently serving state leaders}.
\end{thebibliography}
\end{document}
